---
title: "`r getOption('startr.title')` - The missing PIO"
author: "`r getOption('startr.author')`"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    code_folding: show
    df_print: kable
    self_contained: no
    theme: spacelab
    toc: yes
    toc_depth: 3
editor_options:
  chunk_output_type: inline
---


```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis", collapse = TRUE}

if (!require('upstartr')) install.packages('upstartr'); library('upstartr')

run_config()

source(here::here("R/", "utils.R"))
source(here::here("R/", "functions.R"))
source(here::here("R/", "palette.R"))
source(here::here("R/", "theme.R"))

run_process()
run_analyze()
run_visualize()

```

***



* 69.76 per cent decrease in press conferences between 2018 and 2021
* The number of press conferences was halved in 2020 with a 43.8 per cent decrease from 2019. 
* At a little less than three-quarters of the way through the year, 2021 is on track to set a new record low for the number of WPS press conferences

* Ottawa Police (2016 population 989,657) have issued 553 press releases since 2018 compared to 237 from the Winnipeg Police Service (2016 population 711,925)

*** 

## WPS press conferences


```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis", collapse = TRUE}

plot(wfp_pressers_2018_2021_annual)

plot(wfp_pressers_2018_2021_monthly)

# ggplotly(wfp_pressers_2018_2021_monthly)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis", collapse = TRUE}
datatable(wps_pressers_2018_2021_annual,
  caption = "Table: wps_pressers_2018_2021_annual",
  class = "cell-border stripe",
  rownames = FALSE,
  filter = "top",
  options = list(
    pageLength = 20,
    order = list(list(0, "asc"))
    # language = list(search = 'Filter:'),
    # search = list(regex = TRUE, caseInsensitive = FALSE, search = 'Police')
  )
)

datatable(wps_pressers_2018_2021_monthly_wide,
  caption = "Table: wps_pressers_2018_2021_monthly_wide",
  class = "cell-border stripe",
  rownames = FALSE,
  filter = "top",
  options = list(
    pageLength = 20,
    order = list(list(0, "asc"))
    # language = list(search = 'Filter:'),
    # search = list(regex = TRUE, caseInsensitive = FALSE, search = 'Police')
  )
)

```


## WPS press releases


```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis", collapse = TRUE}

plot(wfp_releases_2018_2021_annual)

plot(wfp_releases_2018_2021_monthly)

```

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis", collapse = TRUE}
datatable(wps_releases_2018_2021_annual,
  caption = "Table: wps_releases_2018_2021_annual",
  class = "cell-border stripe",
  rownames = FALSE,
  filter = "top",
  options = list(
    pageLength = 20,
    order = list(list(0, "asc"))
    # language = list(search = 'Filter:'),
    # search = list(regex = TRUE, caseInsensitive = FALSE, search = 'Police')
  )
)

datatable(wps_releases_2018_2021_monthly_wide,
  caption = "Table: wps_releases_2018_2021_monthly_wide",
  class = "cell-border stripe",
  rownames = FALSE,
  filter = "top",
  options = list(
    pageLength = 20,
    order = list(list(0, "asc"))
    # language = list(search = 'Filter:'),
    # search = list(regex = TRUE, caseInsensitive = FALSE, search = 'Police')
  )
)

```

***

## Crime


### Drug crimes (CDSA)
```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis", collapse = TRUE}
plot(wfp_wps_cdsa_crimes)
```

### Property crimes
```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis", collapse = TRUE}
plot(wfp_wps_property_crimes)
plot(wfp_wps_property_crimes_clearance)
```

### Violent crimes
```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis", collapse = TRUE}
plot(wfp_wps_violent_crimes)
plot(wfp_wps_violent_crimes_clearance)
```

### Clearance rates
```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis", collapse = TRUE}
plot(wfp_winnipeg_wps_annual_reports__clearance_facet)

plot(wfp_wps_cdsa_crimes_clearance)


```


*** 

## Other cities

### Ottawa

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis", collapse = TRUE}

datatable(ottawa_police_pressers_annual,
  caption = "Table: ottawa_police_pressers_annual",
  class = "cell-border stripe",
  rownames = FALSE,
  filter = "top",
  options = list(
    pageLength = 20,
    order = list(list(0, "asc"))
    # language = list(search = 'Filter:'),
    # search = list(regex = TRUE, caseInsensitive = FALSE, search = 'Police')
  )
)

```
